Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-12-04 Tex/Old text/fichacatalog.tex
thesis updated text
Thesis update

\thispagestyle{plain}
\begin{center}
%    \Large
%    \textbf{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
%    
%    \vspace{0.4cm}
%    \large
%    Optimal Sizing and Project Validation
%    
%    \vspace{0.4cm}
%    \textbf{Alessandro Trindade}
%    
    \vspace{0.9cm}
    \textbf{Ficha Catalográfica}
\end{center}
\thispagestyle{plain}
Ficha catalog aqui

>>>>

\thispagestyle{plain}
%\begin{center}
%    \Large
%    \textbf{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
%    
%    \vspace{0.4cm}
%    \large
%    Optimal Sizing and Project Validation
%    
%    \vspace{0.4cm}
%    \textbf{Alessandro Trindade}
%    
%    \vspace{0.9cm}
%    \textbf{Ficha Catalográfica elaborada por Suely O. Moraes - CRB 11/365}
%\end{center}
%
%
\thispagestyle{empty}
\null\vfill

\begin{center}
Ficha Catalográfica elaborada por Suely Oliveira Moraes – CRB 11/365
\begin{tabular}{|p{14.5cm}|}%{p{12cm}}
\hline
\begin{small}
\begin{verbatim}
       Trindade, Alessandro Bezerra.
T833a     Automated verification of stand-alone solar photovoltaic 
       systems: optimal sizing and project validation / Alessandro 
       Bezerra Trindade. Manaus: UFAM, 2019.

         121 fl.: il.: 21 cm

         Orientador: Prof. PhD. Lucas Carvalho Cordeiro

         Tese (Doutorado em Informática) - Universidade Federal do
       Amazonas, Programa de Pós-Graduação em Informática.

         1. Verificação formal. 2. Model checking. 3. Sistemas solares
       fotovoltaicos I. Cordeiro, Lucas Carvalho (Orient.) II. 
       Universidade Federal do Amazonas. III. Título.

                                               CDU 004.02:621.31(043.2)
\end{verbatim}
\end{small}
\\ \hline
\end{tabular}
\end{center}

\thispagestyle{plain}
